\section{Discussion}
% 讨论一下模型的延展性
% 优点
% 我们的模型考虑充分，复杂。考虑了多种情况，并按照最终成果进行了诸多分析
% 缺点
% 可以考虑更多
\subsection{Strength}
The advantages of this model are:
\begin{itemize}
    \item Simple and easy to understand, through some functional relations to solve a variety of complex relationships, eliminating complex and redundant and not too helpful to the actual application of the scene of parameters, so that users can use this model without difficulty.
    \item The fitted data of the model parameters are all top papers found on major academic platforms, which are reliable and authoritative so the fitted results are also very realistic.
    \item The relationship between sunlight and container placement angle is fully considered so that the placement angle also becomes a point to be considered rather than a casual treatment, which is evidence of the degree of insight.
    \item We have taken great care to find papers on various fields, and have used time-tested classical formulas and theorems in the paper, thus ensuring the feasibility of the model.
\end{itemize}
\subsection{Weakness}
The model also has some shortcomings:
\begin{itemize}
    \item Only the shape of the container (rectangular) is considered for its influence on the heat transfer with the external environment and the ventilation and air exchange, and the influence of different weather on these two parts is not fully considered. For example, rainy days will bring the rise of air humidity and water droplets on the surface of the container.
    \item It does not take into account the decline in the efficiency of temperature regulation and light provision caused by the gradual aging of these devices in the course of use, thus increasing energy consumption; and does not take into account the maintenance and replacement of equipment in the long term.
\end{itemize}
\subsection{Future Work}
Considering the shortcomings of the model, we also hope that some improvements can be made in the future:
\begin{itemize}
    \item The weather should also be considered: including consideration of the impact of air humidity on mechanical ventilation and temperature control effect during rainy and snowy days, as well as the existence of water droplets and snowflakes attached to the surface of the container in the evaporation and sublimation on the container surface heat transfer; at the same time, we should also consider the impact of possible typhoon weather in Chongming Island, Shanghai, such as the impact of groundwater on heat dissipation, and how to make The design and manufacture of containers can be more adapted to the climate of the region.
    \item The depreciation of the equipment also needs to be considered. A model of the change of equipment efficiency with time can be established, and the cost of maintenance and renewal can be counted, so that the decision of whether to repair or renew the equipment can be made at an appropriate time, thus making the model more realistic.
\end{itemize}
